Evaluating Variable Importances

### 2019-05-12 Scripts/evaluating_variable_importances.Rmd
editted results script

## Variable Importance Heatmaps for models with distance type predictors (Ranks)

### SMOTE

```{r}
#GM12878

rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_10kb_SMOTE$Feature)
rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_25kb_SMOTE$Feature)
rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_50kb_SMOTE$Feature)
rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_100kb_SMOTE$Feature)

unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
                      union(rfimpvars_gm12878_25kb_SMOTE$Feature,
                            union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
unionannots <- sort(unionannots)

vim.gm12878.smote <- data.frame(Feature=unionannots)

vim.gm12878.smote <- left_join(left_join(left_join(left_join(vim.gm12878.smote,rfimpvars_gm12878_10kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_25kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_50kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_100kb_SMOTE, by="Feature")
names(vim.gm12878.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")

vim.gm12878.smote.ranks <- data.frame(Feature=vim.gm12878.smote$Feature,
									  Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
									  Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
									  Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
									  Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))

rankdata <- cbind(vim.gm12878.smote.ranks$Rank.10kb,
                  vim.gm12878.smote.ranks$Rank.25kb,
				  vim.gm12878.smote.ranks$Rank.50kb,
				  vim.gm12878.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.gm12878.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")	 			  
rankdata <- rankdata[order(rankdata[,1], decreasing = FALSE),]
rankdata <- rankdata[1:20,]

#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
my_palette <- colorRampPalette(c("red", "pink", "white"))(nrow(rankdata))
heatmap.2(t(rankdata),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = TRUE,
          cexRow=1.5,
          cexCol=1.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=1:4,
          colsep=0:nrow(rankdata))

#K562

rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

rfimpvars_K562_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_10kb_SMOTE$Feature)
rfimpvars_K562_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_25kb_SMOTE$Feature)
rfimpvars_K562_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_50kb_SMOTE$Feature)
rfimpvars_K562_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_100kb_SMOTE$Feature)

unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
                      union(rfimpvars_K562_25kb_SMOTE$Feature,
                            union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
unionannots <- sort(unionannots)

vim.K562.smote <- data.frame(Feature=unionannots)

vim.K562.smote <- left_join(left_join(left_join(left_join(vim.K562.smote,rfimpvars_K562_10kb_SMOTE, by="Feature"),
								rfimpvars_K562_25kb_SMOTE, by="Feature"),
								rfimpvars_K562_50kb_SMOTE, by="Feature"),
								rfimpvars_K562_100kb_SMOTE, by="Feature")
names(vim.K562.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")

vim.K562.smote.ranks <- data.frame(Feature=vim.K562.smote$Feature,
									  Rank.10kb=rank(-vim.K562.smote$Importance.10kb, na.last = TRUE),
									  Rank.25kb=rank(-vim.K562.smote$Importance.25kb, na.last = TRUE),
									  Rank.50kb=rank(-vim.K562.smote$Importance.50kb, na.last = TRUE),
									  Rank.100kb=rank(-vim.K562.smote$Importance.100kb, na.last = TRUE))

rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
                  vim.K562.smote.ranks$Rank.25kb,
				  vim.K562.smote.ranks$Rank.50kb,
				  vim.K562.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.K562.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")

#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
heatmap.2(t(rankdata),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 2,
          dendrogram="both",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = TRUE,
          cexRow=1.5,
          cexCol=0.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=1:4,
          colsep=0:nrow(rankdata)) 
```

## Average Variable Importances Heatmaps for models with distance type predictors (Ranks)

```{r}
#gm12878 
##average then rank
vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0

vim.gm12878.smote.ave.rank <- data.frame(Feature=vim.gm12878.smote$Feature,
                                    AveImp=rowMeans(vim.gm12878.smote[,-1]))
vim.gm12878.smote.ave.rank$Rank <- rank(-vim.gm12878.smote.ave.rank$AveImp, na.last = TRUE)
vim.gm12878.smote.ave.rank <- vim.gm12878.smote.ave.rank[order(vim.gm12878.smote.ave.rank$Rank, decreasing = FALSE),]
rankdata.a.r <- cbind(vim.gm12878.smote.ave.rank$Rank,vim.gm12878.smote.ave.rank$Rank)
rankdata.a.r <- rankdata.a.r[1:20,]
rownames(rankdata.a.r) <- vim.gm12878.smote.ave.rank$Feature[1:20]

#my_palette <- colorRampPalette(c("red", "white"))(100)
my_palette_rank <- colorRampPalette(c("red", "white"))(nrow(rankdata.a.r))
heatmap.2(t(rankdata.a.r),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          labRow = "",
          labCol = rownames(rankdata.a.r),
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette_rank,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 2,
          dendrogram="none",     # only draw a row dendrogram,
          Rowv = NA,
          Colv = NA,
          cexRow=1.5,
          cexCol=1.5,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          #lwid=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=c(0,2),
          colsep=0:nrow(rankdata.a.r)
          )

##rank then average
vim.gm12878.smote.rank.ave <- cbind(Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
                                    Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
                                    Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
                                    Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))
rownames(vim.gm12878.smote.rank.ave) <- vim.gm12878.smote$Feature
rankdata.r.a <- rowMeans(vim.gm12878.smote.rank.ave)
rankdata.r.a <- rankdata.r.a[order(rankdata.r.a, decreasing = FALSE)]
rankdata.r.a <- rankdata.r.a[1:20]
rankdata.r.a <- cbind(rankdata.r.a,rankdata.r.a)
heatmap.2(t(rankdata.r.a),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          labRow = "",
          labCol = rownames(rankdata.r.a),
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette_rank,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 2,
          dendrogram="none",     # only draw a row dendrogram,
          Rowv = NA,
          Colv = NA,
          cexRow=1.5,
          cexCol=1.5,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          #lwid=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=c(0,2),
          colsep=0:nrow(rankdata.r.a)
          )

## ICC

```{r}
vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
icc(vim.gm12878.smote, model = "twoway", type = "agreement")

>>>>

# Variable Importance Heatmaps for models with distance type predictors with SMOTE resampling

##GM12878

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
annots <- gsub(paste(c("Gm12878-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]
```

###10kb

```{r}
varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_10kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_10kb) <- NULL
```

###25kb

```{r}
varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_25kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_25kb) <- NULL
```

###50kb

```{r}
varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_50kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_50kb) <- NULL
```

###100kb

```{r}
varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_100kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_100kb) <- NULL
```

##K562

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
annots <- gsub(paste(c("K562-", 
                             "-Haib.bed", 
                             "-Sydh.bed",
                             "-Uta.bed",
                             "-Uw.bed",
                             "-Broad.bed",
                             "-Uchicago.bed"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]
```

###10kb

```{r}
varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_10kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_10kb) <- NULL
```

###25kb

```{r}
varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_25kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_25kb) <- NULL
```

###50kb

```{r}
varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_50kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_50kb) <- NULL
```

###100kb

```{r}
varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_100kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_100kb) <- NULL
```

##Plots

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Transcription Factor") +
  scale_fill_gradient2(low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Transcription Factor") +
  scale_fill_gradient2(low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```
